Positivity-preserving adaptive Runge-Kutta methods: results

### 2020-02-09 latex/overview.tex
New structure of Paper
Changed the order of certain sections in the paper to make it more read- and understandable

\section{Applicable Problems}\label{sec:app_problem}
The approach can be used with ODE systems $u' = f(t,u)$ that ensure  $u(t) \geq 0 \forall_t \forall_{  u_0 \geq 0}$

@@

(Note: Probably it is better to move this section further to the back)

@@

\subsection{Error detection and Approximation}
When changing the weights the solution $u^{n+1}$ is changed. 
By incorporating the Order Conditions for a certain Order the space of $b$ that can be choose is limited to a linear Subspace. 
Now it is important to know if the new solution $u^{n+1}$ still resembles the solution of the ODE $u(t_{n+1})$. 
We can motivate this with the following example:

@@

In \ref{proof:combiningb} it is stated that one can construct the stability function of a RKM  $R_b$  with the weights $b = \alpha b_1 + \beta b_2$ by adding the weighted stability functions $R_{\alpha b_a+\beta b_b}(z) = \alpha R_{\alpha b_a}(z) + \beta R_{\beta b_b}(z) $ where all stability functions have the same $A$ and $\alpha + \beta = 1$.

\subsubsection{Convex Combination}
If the new $b$ is chosen as a convex combination of $b$ it is easy to prove that the resulting  the Region of absolute stability is at least the Intersection of the region of absolute stability of the methods that define the convex combination. (Compare Section\,\ref{proof:convex_comb}). This also means that if all the used embedded methods used to construct the new $b$ are A-Stable, the resulting method is also A-Stable.

\subsubsection{Direct Adaptation}
If the $b$ is adapted directly there is no such proof.
A useful property of the resulting stability region is that it is similar to the stability region of the baseline method. 
(Note: is it possible to give some statement like: If the stability regions of the rkm used for multiple steps are similar, then the overall method is stable for the intersection of the stability regions)

In Section\,\ref{sec:deriv_sr_b} a proof is given that for most methods a small change of $b$ does not alter the stability function dramatically.

(Todo: Maybe a flowchart and a description on how we stitch everything together.)

\section{Useful proofs}

\subsection{Existence of b}
Ensuring a feasible $b$ exists for a certain order condition is in general very difficult.
If we drop the order conditions it is known that there is a positive solution as long as there is a $k_c$ with $k_c \geq 0$.
This is no problem when using a implicit method because a backward euler step always gives a positive solution.

\subsection{Stability function of linear combinations}\label{proof:combiningb}
Let $R_b(z)$ denote the stability function of a RKM method with the butcher tableau

@@

\subsection{Stability of convex combination}\label{proof:convex_comb}

@@

\subsection{Stability of direct adaptation}\label{sec:deriv_sr_b}

@@

>>>>

\subsection{Example I}\label{sec:example_reac}

TODO: Add here the reaction equation, show that it behaves better with the new approach. (still keep it simple with fixed stepsize...)

\subsection{Example II}\label{sec:example_lin}

(Note: The primary goal here is to put the idea of changing the b into perspective. We have shown the general idea and how it works, now we want to discuss on what it does in practice. At first we state it is good to preserve the order... Get to the Example ... and show that there is more to it)

By incorporating the Order Conditions for a certain Order the space of $b$ that can be choose is limited to a linear Subspace. 
Now it is important to know if the new solution $u^{n+1}$ still resembles the solution of the ODE $u(t_{n+1})$. 
We can motivate this with the following example:

@@

@@

\subsection{Error detection and Approximation}
When changing the weights the solution $u^{n+1}$ is changed. 
By incorporating the Order Conditions for a certain Order the space of $b$ that can be choose is limited to a linear Subspace. 
Now it is important to know if the new solution $u^{n+1}$ still resembles the solution of the ODE $u(t_{n+1})$. 
This can be seen in example in section\,\ref{sec:example_lin}.
By a suitable choice of $\alpha \in [\frac{1}{6},\frac{7}{30}]$ any $u$ that complies with mass conservation and positifity can be reached.

@@

The stability function of a RKM  $R_b$  with the weights $b = \alpha b_1 + \beta b_2$ cn be calculated by adding the weighted stability functions $R_{\alpha b_a+\beta b_b}(z) = \alpha R_{\alpha b_a}(z) + \beta R_{\beta b_b}(z) $ where all stability functions have the same $A$ and $\alpha + \beta = 1$.

Let $R_b(z)$ denote the stability function of a RKM method with the butcher tableau

@@

\subsubsection{Stability of convex combination}
If the new $b$ is chosen as a convex combination of $b$ it is easy to prove that the resulting  the Region of absolute stability is at least the Intersection of the region of absolute stability of the methods that define the convex combination. (Compare Section\,\ref{proof:convex_comb}). This also means that if all the used embedded methods used to construct the new $b$ are A-Stable, the resulting method is also A-Stable.

@@

\subsubsection{Stability of  Direct Adaptation}
If the $b$ is adapted directly there is no such proof.
A useful property of the resulting stability region is that it is similar to the stability region of the baseline method. 
(Note: is it possible to give some statement like: If the stability regions of the rkm used for multiple steps are similar, then the overall method is stable for the intersection of the stability regions)

For most methods a small change of $b$ does not alter the stability function dramatically.

@@

TODO: Discuss in this section aspects that are needed for implementation (and improve the usability) but do not concern the mathematical idea of the approach.

\subsection{•}
(Todo: Maybe a flowchart and a description on how we stitch everything together.)

\subsection{Applicable Problems}\label{sec:app_problem}
The approach can be used with ODE systems $u' = f(t,u)$ that ensure  $u(t) \geq 0 \forall_t \forall_{  u_0 \geq 0}$
